An Improved ANS Transaction Template

### 2018-01-26 paper.tex
not inspired/tired... stopping for the night
starting case 1 description

>>>>

\section{Results}

\subsection{Assays}
\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.

This bump in enrichment can easily be explained, as the cascade don't have the
same number of stages, there is less stripping enrichment work, than enriching
work. That is to say that even work in an ideal case (where the stripping work of a
stage is the exact inverse of the enrich work), with an cascade with less
stripping stage than enriching stage will produce tail with a higher enrichment
than the feed of the previous level of
